To carry out cluster analysis, we need to generate a document-term matrix. 
We call all the email text from one receiver a document, we cleaned and transformed the text by 
\begin{enumerate}
\item Convert into lower case. Remove problematic symbols, punctuations and numbers.
\item Remove stop words including 'date', 'can', 'we', 'will' etc. Remove words that are typical in the emails including 'message','sent','original' etc and receivers' names.
\begin{itemize}
\item The cleaned text like "... president nightmare scenarios panetta persuaded renditions tool worth keeping rendition program began carefully monitored form clinton administration bush years transformed ..."
\end{itemize}
\item Convert all documents into a document-term matrix
\begin{itemize} 
\item The matrix has 10 rows representing each email receiver's account; and 20792 columns representing unique words that have appeared in all the email text
\item In each row, if a certain word appears N times the corresponding column would have 'N' , '0' if not. The sparsity of the matrix is 74\%, the non-/sparse entries are 53249/155201. 
\end{itemize}
\item Compute Euclidean distance between each documents.
\end{enumerate}
The distance between documents is defined in 20792 dimensional space. To illustrate for instance, if we have two documents Doc1 (house,libya, document) and Doc 2 (house, information, release, document). In the document-term matrix, the two documents is represented by word frequency eg. we can have Doc1=(1, 0, 1, 1), Doc2=(1, 1, 2, 1), the distance between Doc1 and Doc 2 will hence be $\sqrt{(1-1)^{2} + (0-1)^{2} + (1-2)^{2} + (1-1)^{2}} = \sqrt{2}$.

