To carry out Cluster Analysis, we need to generate a document-term matrix \cite{document-term2015}. 
We compiled for each receiver the emails they received together into a document and then cleaned and transformed the text through the following steps:
\begin{enumerate}
\item Convert into lower case. Remove problematic symbols, punctuations and numbers.
\item Remove stop words including 'date', 'can', 'we', 'will' etc. Remove words that are typical in the emails including 'message','sent','original' etc and receivers' names, so that we have documents like:
\begin{itemize}
\item eg., ``... president nightmare scenarios panetta persuaded renditions tool worth keeping rendition program began carefully monitored form clinton administration bush years transformed ...''
\end{itemize}
\item Convert all documents into a document-term matrix.
\begin{itemize} 
\item The matrix has 10 rows representing each email receiver's account; and 20792 columns representing unique words that have appeared in all the email text.
\item In each row, if a certain word appears N times the corresponding column would have `N' , `0' if it never appears. The sparsity of the matrix is 74\%, with the count of non-zero entries to zero entries being 53249/155201. 
\end{itemize}
\item Compute Euclidean distance between each pair of documents.
\end{enumerate}
The distance between documents is defined in 20792 dimensional space. To illustrate for instance, suppose we have two documents Doc1 (house, libya, document) and Doc 2 (house, information, release, document). In the document-term matrix, the two documents would be represented by word frequency, eg., we would have Doc1 = (1, 0, 1, 1), Doc2 = (1, 1, 2, 1). The distance between Doc1 and Doc 2 would then be $\sqrt{(1-1)^{2} + (0-1)^{2} + (1-2)^{2} + (1-1)^{2}} = \sqrt{2}$.

